Invariant Representations for Noisy Speech Recognition

### 2016-10-23 paper.tex
Address K's comments

    The main idea of generative adversarial
    training is to stack the discriminator and generator network on top of each other and propagate the gradient of the discriminator
    network further to the generator network. In other words, these two networks are competing with each other. The 
    generator is trying to deceive the discriminator network, while the discriminator tries
    to do its best to recognize if there was a deception, similar to adversarial game-theoretic settings.    
    Formally, the objective function of GAN training is
    \begin{align*}
        \min_G \max_D V(D, G) = \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + 
            \mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}
	{\bf Please explain how the min-max applies to the two terms. I assume that we are maximizing first term with respect to D and doing min over D/max over G for the second term. Hence maximizing the first term increases the likelihood of the discriminator output (single sigmoid neuron) for true training data. Maximizing the second term decreases the likelihood of the discriminator output for fake training data. But then, what does the min over G mean? That you are maximizing the generator likelihood of the fake data?}

    In practice, GANs might be hard to train due to the fact that when 
    the discriminator is more powerful that the generator, the latter doesn't 
    receive any gradient and thus can not be improved. One way to solve this problem is to
    use a smart schedule which stops trainign the discriminator as soon as it
    is much better trained than the generator. Other possible solutions include ``soft''
    targets for the discriminator and using a 
    different proxy for the cost {\bf I don't understand different proxy for the cost}.

@@

    {\bf We need to write a couple of sentences on how this is motivated by GAN.} Prior work by~\cite{ganin2014unsupervised} proposed a method of training a network 
    which can be adapted to new domains. The training set consists of the images
    labeled with classes of interest and separate domain labels. For example, the domain may refer to image background. The testing set does not need
    to have the domain labels. The network has a fork-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn the hidden 
    representation that is invariant to the domain labels and performs well on the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time.

@@

\section{Related Work}
    Earlier approaches include various works on denoising including

@@

\section{Experiments}
\label{sec:experiments}
We experimentally evaluate the approach discussed in Section~\ref{sec:gradient-reverse} 
on the Aurora-4~\cite{parihar2002aurora} noisy speech recognition dataset. Aurora-4
is based on the Wall Street Journal corpus (WSJ0). It contains noises of 
six categories which was added to clean
data. Every clean and noisy utterance is filtered to simulate sampling frequency {\bf simulate sampling frequency?}. The training
set contains approximately 4400 clean utterances and 446 utterances of each noise condition,
i.e. a total of 2676 noisy utterances.
The testing
set contains clean data, data corrupted by the 6 noises, and data recorded with a different microphone
for both clean and noisy cases.

@@

    {\bf We need to make the message of this paragraph more clear.}The task of speech recognition differs from the image recognition
    adaptation in an aspect of the domain adaptation network training dynamics. 
    While the most common problem for the GAN type of networks trained on images 
    is overfitting, the noise type classification networks suffers from 
    underfitting. This makes the gradient of the $L_3$ term in Eq.~\ref{eq:cost}
    unrealiable and noisy.

>>>>

    The main idea of generative adversarial
    training is to stack the discriminator and generator network on top of each other and propagate the gradient of the discriminator
    network further to the generator network. In other words, these two networks are competing with each other. The 
    generator is trying to deceive the discriminator network, while the discriminator tries
    to do its best to recognize if there was a deception, similar to adversarial game-theoretic settings.    
    Formally, the objective function of GAN training is
    \begin{align*}
        \min_G \max_D V(D, G) = \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + 
            \mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}
    The maximization over the discriminator $D$ forms a usuall cross-entropy objective, the gradients are
    computed with respect to the parameters of $D$. The parameters of $G$ are minimized using the gradients
    propagated through the second term. The minimization over $G$ makes it to produce examples which $D$
    classifiers as the training ones.
	%{\bf Please explain how the min-max applies to the two terms. I assume that we are maximizing first term with respect to D and doing min over D/max over G for the second term. Hence maximizing the first term increases the likelihood of the discriminator output (single sigmoid neuron) for true training data. Maximizing the second term decreases the likelihood of the discriminator output for fake training data. But then, what does the min over G mean? That you are maximizing the generator likelihood of the fake data?}
    % Dima: deleted paragraph and explained min-max

@@

    %{\bf We need to write a couple of sentences on how this is motivated by GAN.} 
    %Dima: added a sentence at the end of this paragraph
    Prior work by~\cite{ganin2014unsupervised} proposed a method of training a network 
    which can be adapted to new domains. The training set consists of the images
    labeled with classes of interest and separate domain labels. For example, the domain may refer to image background. The testing set does not need
    to have the domain labels. The network has a fork-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn the hidden 
    representation that is invariant to the domain labels and performs well on the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Like the GAN objective forces the generation distribution be close to the data distribution,
    the gradient reverse method makes domain distributions similar to each other.

@@

\section{Related Work}
    Generative adversarial networks were proposed and experimentally evaluated 
    in~\cite{goodfellow2014generative}. This work was continued 
    in work of~\cite{radford2015unsupervised}, which proposes several practical guidelines
    for training GANs. This direction is further explored in~\cite{salimans2016improved}.

    The conditioned GAN for generation task were utilized in~\cite{denton2015deep}. This
    work proposes to improve images increasing the resolution step-by-step. 
    The domain adaptation with the gradient reverse method was proposed in~\cite{ganin2014unsupervised}.

    %TODO: cite denoising papers? some work on aurora 4?

@@

\section{Experiments}
\label{sec:experiments}
We experimentally evaluate the approach discussed in Section~\ref{sec:gradient-reverse} 
on the Aurora-4~\cite{parihar2002aurora} noisy speech recognition dataset. Aurora-4
is based on the Wall Street Journal corpus (WSJ0). It contains noises of 
six categories which was added to clean
data. Every clean and noisy utterance is filtered to simulate the frequency characteristics of the sampling frequency. 
% Dima: is it correct now?
%
The training
set contains approximately 4400 clean utterances and 446 utterances of each noise condition,
i.e. a total of 2676 noisy utterances.
The testing
set contains clean data, data corrupted by the 6 noises, and data recorded with a different microphone
for both clean and noisy cases.

@@

    %{\bf We need to make the message of this paragraph more clear.}
    % Dima: tried to fix -- it is differnt => needs more investigation
    Our experiments show that in contrast to the image recognition task,
    the task of speech recognition,  the domain adaptation network suffers from
    the underfitting. Therefore, the gradient of the $L_3$ term in Eq.~\ref{eq:cost}
    unrealiable and noisy. This aspect needs further development.
